Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
clarify RESET test power

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - RESET test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$ with comparison to the power of an exact test - RESET test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively.
For the RESET test, we included different power of fitted values as proxies. According to [@ramsey_tests_1969], there is no general rule for the power of the fitted values needed by the RESET test, but it found power up to four is usually sufficient. Thus, we followed this guidline to conduct the RESET test.

At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residuals plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
clarify RESET test power

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\) with comparison to the power of an exact test - RESET test,
and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. At the bottom of the figure
\ref{fig:polypower}, there are a sequence of example residuals plots
with increasing levels of \(log_e(E)\). Readers can evaluate them from
left to right and determine at which level the departure from a good
residual plot becomes detectable.

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\) with comparison to the power of an exact test - RESET test,
and two other residual-based conventional tests commonly used in
regression diagnostics but for testing heteroskedasticity and
non-normality respectively. For the RESET test, we included different
power of fitted values as proxies. According to
\citep{ramsey_tests_1969}, there is no general rule for the power of the
fitted values needed by the RESET test, but it found power up to four is
usually sufficient. Thus, we followed this guidline to conduct the RESET
test.

At the bottom of the figure \ref{fig:polypower}, there are a sequence of
example residuals plots with increasing levels of \(log_e(E)\). Readers
can evaluate them from left to right and determine at which level the
departure from a good residual plot becomes detectable.
